---
title: "Business Intelligence Lab Submission Markdown"
author: "<Specify your name here>"
date: "<Specify the date when you submitted the lab>"
output:
  github_document: 
    toc: yes
    toc_depth: 4
    fig_width: 6
    fig_height: 4
    df_print: default
editor_options:
  chunk_output_type: console
---

# Student Details

+---------------------------------------------------+---------------------------------------------+
| **Student ID Numbers and Names of Group Members** | 131038 Doreen Muema                         |
|                                                   |                                             |
|                                                   | 19630 Venus Karanja                         |
|                                                   |                                             |
|                                                   | 135844 Mercy Macharia                       |
|                                                   |                                             |
|                                                   | Ryan Shuma                                  |
|                                                   |                                             |
|                                                   | Bill Akide                                  |
+---------------------------------------------------+---------------------------------------------+
| **BBIT 4.2 Group**                                | A,A,A,B,C                                   |
+---------------------------------------------------+---------------------------------------------+
| **Course Code**                                   | BBT4206                                     |
+---------------------------------------------------+---------------------------------------------+
| **Course Name**                                   | Business Intelligence II                    |
+---------------------------------------------------+---------------------------------------------+
| **Program**                                       | Bachelor of Business Information Technology |
+---------------------------------------------------+---------------------------------------------+
| **Semester Duration**                             | 21^st^ August 2023 to 28^th^ November 2023  |
+---------------------------------------------------+---------------------------------------------+

# Setup Chunk

**Note:** the following KnitR options have been set as the global defaults:\
`knitr::opts_chunk$set(echo = TRUE, warning = FALSE, eval = TRUE,                        collapse = FALSE, tidy = TRUE)`.

> output:\
> \
> github_document:\
> toc: yes\
> toc_depth: 4\
> fig_width: 6\
> fig_height: 4\
> df_print: default\
> \
> editor_options:\
> chunk_output_type: console

More KnitR options are documented here <https://bookdown.org/yihui/rmarkdown-cookbook/chunk-options.html> and here <https://yihui.org/knitr/options/>.

```{r setup, include=FALSE}
library(formatR)
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, eval = TRUE,
                      collapse = FALSE, tidy = TRUE)
```

# Loading Dataset

***Describe the code chunk here:*** Commands to loading Dataset

```{r Your Second Code Chunk}
student_performance_dataset <- readr::read_csv("data/StudentPerformance.csv",
    col_types = readr::cols(class_group = readr::col_factor(levels = c("A", "B",
        "C")), gender = readr::col_factor(levels = c("1", "0")), YOB = readr::col_date(format = "%Y"),
        regret_choosing_bi = readr::col_factor(levels = c("1", "0")), drop_bi_now = readr::col_factor(levels = c("1",
            "0")), motivator = readr::col_factor(levels = c("1", "0")), read_content_before_lecture = readr::col_factor(levels = c("1",
            "2", "3", "4", "5")), anticipate_test_questions = readr::col_factor(levels = c("1",
            "2", "3", "4", "5")), answer_rhetorical_questions = readr::col_factor(levels = c("1",
            "2", "3", "4", "5")), find_terms_I_do_not_know = readr::col_factor(levels = c("1",
            "2", "3", "4", "5")), copy_new_terms_in_reading_notebook = readr::col_factor(levels = c("1",
            "2", "3", "4", "5")), take_quizzes_and_use_results = readr::col_factor(levels = c("1",
            "2", "3", "4", "5")), reorganise_course_outline = readr::col_factor(levels = c("1",
            "2", "3", "4", "5")), write_down_important_points = readr::col_factor(levels = c("1",
            "2", "3", "4", "5")), space_out_revision = readr::col_factor(levels = c("1",
            "2", "3", "4", "5")), studying_in_study_group = readr::col_factor(levels = c("1",
            "2", "3", "4", "5")), schedule_appointments = readr::col_factor(levels = c("1",
            "2", "3", "4", "5")), goal_oriented = readr::col_factor(levels = c("1",
            "0")), spaced_repetition = readr::col_factor(levels = c("1", "2", "3",
            "4")), testing_and_active_recall = readr::col_factor(levels = c("1",
            "2", "3", "4")), interleaving = readr::col_factor(levels = c("1", "2",
            "3", "4")), categorizing = readr::col_factor(levels = c("1", "2", "3",
            "4")), retrospective_timetable = readr::col_factor(levels = c("1", "2",
            "3", "4")), cornell_notes = readr::col_factor(levels = c("1", "2", "3",
            "4")), sq3r = readr::col_factor(levels = c("1", "2", "3", "4")), commute = readr::col_factor(levels = c("1",
            "2", "3", "4")), study_time = readr::col_factor(levels = c("1", "2",
            "3", "4")), repeats_since_Y1 = readr::col_integer(), paid_tuition = readr::col_factor(levels = c("0",
            "1")), free_tuition = readr::col_factor(levels = c("0", "1")), extra_curricular = readr::col_factor(levels = c("0",
            "1")), sports_extra_curricular = readr::col_factor(levels = c("0", "1")),
        exercise_per_week = readr::col_factor(levels = c("0", "1", "2", "3")), meditate = readr::col_factor(levels = c("0",
            "1", "2", "3")), pray = readr::col_factor(levels = c("0", "1", "2", "3")),
        internet = readr::col_factor(levels = c("0", "1")), laptop = readr::col_factor(levels = c("0",
            "1")), family_relationships = readr::col_factor(levels = c("1", "2",
            "3", "4", "5")), friendships = readr::col_factor(levels = c("1", "2",
            "3", "4", "5")), romantic_relationships = readr::col_factor(levels = c("0",
            "1", "2", "3", "4")), spiritual_wellnes = readr::col_factor(levels = c("1",
            "2", "3", "4", "5")), financial_wellness = readr::col_factor(levels = c("1",
            "2", "3", "4", "5")), health = readr::col_factor(levels = c("1", "2",
            "3", "4", "5")), day_out = readr::col_factor(levels = c("0", "1", "2",
            "3")), night_out = readr::col_factor(levels = c("0", "1", "2", "3")),
        alcohol_or_narcotics = readr::col_factor(levels = c("0", "1", "2", "3")),
        mentor = readr::col_factor(levels = c("0", "1")), mentor_meetings = readr::col_factor(levels = c("0",
            "1", "2", "3")), `Attendance Waiver Granted: 1 = Yes, 0 = No` = readr::col_factor(levels = c("0",
            "1")), GRADE = readr::col_factor(levels = c("A", "B", "C", "D", "E"))),
    locale = readr::locale())
```

# Dimensions

***Describe the next code chunk here:*** Commands to display the dimensions of the datasets

```{r Your 3th Code Chunk}
dim(student_performance_dataset)
```

# Data Types

***Describe the next code chunk here:*** Command to identify the data types

```{r Your 4th Code Chunk}
result <- sapply(student_performance_dataset, class)
for (i in seq_along(result)) {
  cat(sprintf("%-50s %s\n", names(result)[i], result[[i]]))
}


```

# Descriptive Statistics

## Measures of Frequency

***Describe the next code chunk here:*** is used to calculate and display the frequency and percentage distribution of the "gender" variable in the "student_performance_dataset."

```{r Your 5th Code Chunk}
gender_freq <- student_performance_dataset$gender
cbind(frequency = table(gender_freq),
    percentage = prop.table(table(gender_freq)) * 100)
```

## Measures of Central Tendency

***Describe the next code chunk here:*** calculates the mode (most frequent value) of the "EXAM: x/60 (60%)" column in the "student_performance_dataset" and prints the result.

```{r Your 6th Code Chunk}
student_performance_dataset_mode <- names(table(student_performance_dataset$`EXAM: x/60 (60%)`))[
  which(table(student_performance_dataset$`EXAM: x/60 (60%)`) == max(table(student_performance_dataset$`EXAM: x/60 (60%)`)))
]
print(student_performance_dataset_mode)
```

## Measures of Distribution/Dispersion/Spread/Scatter/Variability

```{r Your 7th Code Chunk}
summary(student_performance_dataset)
```

### Measure the variance

***Describe the next code chunk here:*** calculates the variance of each numeric column, disregarding missing values (NAs), and t

```{r Your 8th Code Chunk}
library(dplyr)
library(tidyr)

numeric_columns <- student_performance_dataset %>%
  select_if(is.numeric)

variance_df <- numeric_columns %>%
  summarise_all(~ var(., na.rm = TRUE)) %>%
  pivot_longer(everything(), names_to = "Column", values_to = "Variance")

print(variance_df, n = Inf)
```

### Measure the standard deviation

***Describe the next code chunk here:*** calculates the standard deviation for "EXAM: x/60 (60%)" column

```{r Your 9th Code Chunk}
standard_deviation <- sd(student_performance_dataset$`EXAM: x/60 (60%)`, na.rm = TRUE)

print(standard_deviation)
```

# Inferential Statistics

## Perform ANOVA 

***Describe the next code chunk here:***code is conducting a two-way Analysis of Variance (ANOVA) to analyze the effects of two categorical independent variables, class_group and gender, on the dependent variable Average Course Evaluation Rating.

```{r Your 10th Code Chunk}
student_performance_dataset_anova <- aov(`Average Course Evaluation Rating` ~ class_group + gender, data = student_performance_dataset)

summary(student_performance_dataset_anova)

```

# Qualitative Data Analysis

## Univariate Plots

### Create Histograms

***Describe the next code chunk here:*** code generates histograms for three different variables ("project_score," "exam_score," and "course_score")

```{r Your 11th Code Chunk}
project_score <- as.numeric(student_performance_dataset$`Project: (10%): x/30 x 100 TOTAL`)
exam_score <- as.numeric(student_performance_dataset$`EXAM: x/60 (60%)`)
course_score <- as.numeric(student_performance_dataset$`Coursework TOTAL: x/40 (40%)`)

course_score <- course_score[!is.na(course_score)]

par(mfrow = c(2, 2))

# Create a histogram for study time
hist(project_score, 
     main = "Histogram of Project Scores",
     xlab = "Project Scores",
     ylab = "Frequency",
     col = "skyblue",  
     border = "black",  
     breaks = 10) 

# Create a histogram for exam scores
hist(exam_score, 
     main = "Histogram of Exam Scores",
     xlab = "Exam Scores",
     ylab = "Frequency",
     col = "green",  
     border = "black",  
     breaks = 10) 

# Create a histogram for quiz scores (after removing missing values)
hist(course_score, 
     main = "Histogram of Quiz Scores",
     xlab = "Quiz Scores",
     ylab = "Frequency",
     col = "orange",  
     border = "black",  
     breaks = 10)  

```

### Missingness Map

***Describe the next code chunk here:***checks for missing data patterns in the "student_performance_dataset"

```{r Your 12th Code Chunk}
if (!is.element("Amelia", installed.packages()[, 1])) {
  install.packages("Amelia", dependencies = TRUE)
}
require("Amelia")

# Create a missing data pattern plot for student_performance_dataset
missmap(student_performance_dataset, col = c("red", "green"), legend = TRUE)
```

## Multivariate Plots

### Create a Scatter Plot

***Describe the next code chunk here:*** creates a scatter plot that visualizes the relationship between "Study Time" and "Average Course Evaluation Rating" for the dataset

```{r Your 13th Code Chunk}
library(ggplot2)

ggplot(student_performance_dataset, aes(x = study_time, y = `Average Course Evaluation Rating`)) +
  geom_point() +
  labs(x = "Study Time", y = "Average Course Evaluation Rating") +
  ggtitle("Scatter Plot: Study Time vs. Average Course Evaluation Rating")

```

```{r Your 14th Code Chunk}
renv::snapshot()
```

