---
title: "Business Intelligence Lab Submission Markdown"
author: "<Specify your name here>"
date: "<Specify the date when you submitted the lab>"
output:
  github_document: 
    toc: yes
    toc_depth: 4
    fig_width: 6
    fig_height: 4
    df_print: default
editor_options:
  chunk_output_type: console
---

# Student Details

+---------------------------------------------------+---------------------------------------------+
| **Student ID Numbers and Names of Group Members** | 131038 Doreen Muema                         |
|                                                   |                                             |
|                                                   | 19630 Venus Karanja                         |
|                                                   |                                             |
|                                                   | 135844 Mercy Macharia                       |
|                                                   |                                             |
|                                                   | Ryan Shuma                                  |
|                                                   |                                             |
|                                                   | Bill Akide                                  |
+---------------------------------------------------+---------------------------------------------+
| **BBIT 4.2 Group**                                | A,A,A,B,C                                   |
+---------------------------------------------------+---------------------------------------------+
| **Course Code**                                   | BBT4206                                     |
+---------------------------------------------------+---------------------------------------------+
| **Course Name**                                   | Business Intelligence II                    |
+---------------------------------------------------+---------------------------------------------+
| **Program**                                       | Bachelor of Business Information Technology |
+---------------------------------------------------+---------------------------------------------+
| **Semester Duration**                             | 21^st^ August 2023 to 28^th^ November 2023  |
+---------------------------------------------------+---------------------------------------------+

# Setup Chunk

**Note:** the following KnitR options have been set as the global defaults:\
`knitr::opts_chunk$set(echo = TRUE, warning = FALSE, eval = TRUE,                        collapse = FALSE, tidy = TRUE)`.

> output:\
> \
> github_document:\
> toc: yes\
> toc_depth: 4\
> fig_width: 6\
> fig_height: 4\
> df_print: default\
> \
> editor_options:\
> chunk_output_type: console

More KnitR options are documented here <https://bookdown.org/yihui/rmarkdown-cookbook/chunk-options.html> and here <https://yihui.org/knitr/options/>.

```{r setup, include=FALSE}
library(formatR)
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, eval = TRUE,
                      collapse = FALSE, tidy = TRUE)
```

# Loading Dataset

***Describe the code chunk here:*** Commands to loading Dataset

```{r Your Second Code Chunk}
student_performance_dataset <- readr::read_csv("data/StudentPerformance.CSV",
    col_types = readr::cols(class_group = readr::col_factor(levels = c("A", "B",
        "C")), gender = readr::col_factor(levels = c("1", "0")), YOB = readr::col_date(format = "%Y"),
        regret_choosing_bi = readr::col_factor(levels = c("1", "0")), drop_bi_now = readr::col_factor(levels = c("1",
            "0")), motivator = readr::col_factor(levels = c("1", "0")), read_content_before_lecture = readr::col_factor(levels = c("1",
            "2", "3", "4", "5")), anticipate_test_questions = readr::col_factor(levels = c("1",
            "2", "3", "4", "5")), answer_rhetorical_questions = readr::col_factor(levels = c("1",
            "2", "3", "4", "5")), find_terms_I_do_not_know = readr::col_factor(levels = c("1",
            "2", "3", "4", "5")), copy_new_terms_in_reading_notebook = readr::col_factor(levels = c("1",
            "2", "3", "4", "5")), take_quizzes_and_use_results = readr::col_factor(levels = c("1",
            "2", "3", "4", "5")), reorganise_course_outline = readr::col_factor(levels = c("1",
            "2", "3", "4", "5")), write_down_important_points = readr::col_factor(levels = c("1",
            "2", "3", "4", "5")), space_out_revision = readr::col_factor(levels = c("1",
            "2", "3", "4", "5")), studying_in_study_group = readr::col_factor(levels = c("1",
            "2", "3", "4", "5")), schedule_appointments = readr::col_factor(levels = c("1",
            "2", "3", "4", "5")), goal_oriented = readr::col_factor(levels = c("1",
            "0")), spaced_repetition = readr::col_factor(levels = c("1", "2", "3",
            "4")), testing_and_active_recall = readr::col_factor(levels = c("1",
            "2", "3", "4")), interleaving = readr::col_factor(levels = c("1", "2",
            "3", "4")), categorizing = readr::col_factor(levels = c("1", "2", "3",
            "4")), retrospective_timetable = readr::col_factor(levels = c("1", "2",
            "3", "4")), cornell_notes = readr::col_factor(levels = c("1", "2", "3",
            "4")), sq3r = readr::col_factor(levels = c("1", "2", "3", "4")), commute = readr::col_factor(levels = c("1",
            "2", "3", "4")), study_time = readr::col_factor(levels = c("1", "2",
            "3", "4")), repeats_since_Y1 = readr::col_integer(), paid_tuition = readr::col_factor(levels = c("0",
            "1")), free_tuition = readr::col_factor(levels = c("0", "1")), extra_curricular = readr::col_factor(levels = c("0",
            "1")), sports_extra_curricular = readr::col_factor(levels = c("0", "1")),
        exercise_per_week = readr::col_factor(levels = c("0", "1", "2", "3")), meditate = readr::col_factor(levels = c("0",
            "1", "2", "3")), pray = readr::col_factor(levels = c("0", "1", "2", "3")),
        internet = readr::col_factor(levels = c("0", "1")), laptop = readr::col_factor(levels = c("0",
            "1")), family_relationships = readr::col_factor(levels = c("1", "2",
            "3", "4", "5")), friendships = readr::col_factor(levels = c("1", "2",
            "3", "4", "5")), romantic_relationships = readr::col_factor(levels = c("0",
            "1", "2", "3", "4")), spiritual_wellnes = readr::col_factor(levels = c("1",
            "2", "3", "4", "5")), financial_wellness = readr::col_factor(levels = c("1",
            "2", "3", "4", "5")), health = readr::col_factor(levels = c("1", "2",
            "3", "4", "5")), day_out = readr::col_factor(levels = c("0", "1", "2",
            "3")), night_out = readr::col_factor(levels = c("0", "1", "2", "3")),
        alcohol_or_narcotics = readr::col_factor(levels = c("0", "1", "2", "3")),
        mentor = readr::col_factor(levels = c("0", "1")), mentor_meetings = readr::col_factor(levels = c("0",
            "1", "2", "3")), `Attendance Waiver Granted: 1 = Yes, 0 = No` = readr::col_factor(levels = c("0",
            "1")), GRADE = readr::col_factor(levels = c("A", "B", "C", "D", "E"))),
    locale = readr::locale())
```


```{r Your 16th Code Chunk}
```

**etc.** as per the lab submission requirements.
